\documentclass[a4paper,10pt]{report} %for type of document
\usepackage[utf8x]{inputenc} %for input technique
\usepackage[pdftex]{graphicx} %for inserting images

% Title Page
\title{Software Lab \\Assignment-3}
\author{Pratyush Anand \\2010EEY7515 \\C.Tech, IITD}


\begin{document}
  \maketitle

  \chapter{Problem Statement}
    Generate UML diagrams for following scenarios
\begin{itemize}
 \item Use case Diagram
 \item Sequence Diagram
 \item Class Diagram
\end{itemize}

  \chapter{Operation}
\subsection {Assumptions}
\begin{itemize}
\item Middleware software also contains family patient portal
\item Accounting software has been considered as an external agent.
\end{itemize}
\subsection {Use case Diagram}
\begin{itemize}
\item All the external part of the system has been represented as
actors and has been kept outside the rectangular boundary, while all use
cases has been kept inside the rectangular boundary. So, following
actors has been identified. \\ \\
Doctor : Can view notifications on hid PDA  and visits patient's room\\
Views Patient's report and updates it.\\
Orders test if required.\\
Can view appointment request.\\
Can grant appointment to relative. \\ \\
Nurse:Can view Notification \\
Can see triage list and prioritize service.\\
can see doctor's Location\\ \\
Accounting Application: Can bill doctors visit \\
Can bill ordered test.\\ \\
Relatives: Can see doctor's presence. \\
Can request doctor's appointment. \\
Can connect Doctor. \\ \\
Sensors: Can monitor patient and can generate and alarm. \\ \\
Patient: Can see doctors presence and can raise alarm \\ \\

Other than the above <<extend>> use cases some has been taken as
<<uses>> use cases. \\
Determining Location and issue interrupt: This will be used by most of
the use cases as shown in use case diagram.\\
Similarly other <<uses>> use cases are also used by other use cases.
\end{itemize}
   
\subsection {Class Diagram}
\begin{itemize}
\item objects defined in sequence diagram has been represented here with
its attributes and methods.
\item Here, it is clearly visible that middleware software is the
central agency with whom every one interacts. For example, doctor,
nurse and patient all are updating their location continuously.So they
will just call send\_location and update\_location\_for\_all will update
the location. Now this updated location can be viewed by either calling
view\_doctors\_presence or view\_patients\_location.
\item Class Doctor: It has following attributes: \\
Location: It will have information about his location. \\
Name: Will have doctor's name.\\
ID: Will have employee ID.\\
This class has following operations. \\
view\_report: Can view report of the patient. \\
update\_report: It can also invalidate and update report.\\
order\_test: It can order test if required. \\
view\_appointment: Can view appointment requested by relatives.
grant\_appointment: Can grant appointment to relative. \\
view\_emergency\_notifications: View alerts generated by either patient
or sensor. \\
send\_location: will always sends its location.
\item Class Nurse: It has following attributes: \\
Location: It will have information about her location. \\
Name: Will have nurse's name.\\
ID: Will have employee ID.\\
This class has following operations. \\
view\_emergency\_notifications: View alerts generated by either patient
or sensor. \\
send\_location: will always sends its location.\\
view\_triage\_list:Can see all the list.\\
prioritize\_service: Can prioritize on need basis.\\
view\_doctors\_location: Can see doctor's location by passing his IDs.\\
thank\_others: Can thank other nurse by passing her ID.\\
\item Class Patient: It has following attributes: \\
Location: It will have information about her location. \\
Name: Will have his name.\\
ID: Will have patient ID.\\
This class has following operations. \\
view\_doctors\_presence: Can view if doctor is making a round.
generate\_alarm: Can generate alarm in case of emergency.
send\_location: will always sends its location.\\
\item Class Accounting Application:This class has following operations. \\
bill\_doctors\_visit: bill for each visit of doctor.
bill\_ordered\_test: Bill for each test ordered by doctor. \\
\item Class relative: It has following operations. \\
view\_doctors\_presence: Can view if doctor is making a round.\\
request\_appointment: Can request appointment from doctor.\\
connect\_doctor: Can connect to doctor if appointment granted. \\
\item Class sensors: It has following operations. \\
monitor\_patient: can monitor patient's health. \\
generate\_alarm: Can generate alarm in case of emergency. \\
\item Class Middleware Software: It has following operations. \\
generate\_report: Will sense doctor's presence in patient's room and
will generate patient's report for the doctor.\\
update\_test\_request: Will update test request if it is done by doctor,
and will send updated request to accounting system.\\
update\_request\_appointment: sends appointment information to doctor.
\\
update\_granted\_appointment: Sends granted appointment information to
relatives. \\
update\_location\_for\_all: update location database and send interrupt
to doctor.\\
receive\_and\_send\_private\_messages: Receive and send messages like
thanks. \\
receive\_and\_generate\_emergency\_requests: \\
update\_doctors\_visit: send doctors visit to accounting systems.


\end{itemize}
\subsection {Sequence Diagram}
\begin{itemize}
\item All the actors of use cases along with  middleware software has
been taken as objects.
\item All objects asks for required information from middleware
software. They also send the updated information to middleware software.
\end{itemize}
 
\end{document}          
