\documentclass[a4paper,10pt]{report} %for type of document
\usepackage[utf8x]{inputenc} %for input technique
\usepackage[pdftex]{graphicx} %for inserting images

% Title Page
\title{Software Lab \\Assignment-2}
\author{Pratyush Anand \\2010EEY7515 \\C.Tech, IITD}


\begin{document}
  \maketitle

  \chapter{Problem Statement}
    Write code for Library Management System.

  \chapter{Specifications}
    \begin{enumerate}
      \item When code is run, it will promt for login. A default login
with name 'admin' and password 'admin' will be created. Admin password can be
changed by the customer.
      \newline
      \item Admin can add an user with two kinds of right, librarian and
member. Rights for librarian and member will be defined according to the
problem statement.
      \newline
      \item One can also login with 'guest' and will not require a
password. He/she will have same rights as defined for public in problem
statement.
      \newline
	\item After login one can see menus according to his defined
rights. Menus would be:
    \begin{itemize}
	 \item Log-Out
	 \item Search Data Base
	 \item Change Password
	 \item Borrow Book
	 \item Add Book
	 \item Add Members
    \end{itemize}
	A guest will see only first 2, member will see first 4 and librarian
will see all menus.
	\item Selecting the desired menu respective functionalities will
be executed. 
    \end{enumerate}

  \chapter{Operation}
	Enum for rights will be created:\\
	enum rights \{\\
		LIBRARIAN,\\
		MEMBER,\\
		GUEST,\\
	\}\\

	A structure will be created as the info for member.\\
	struct member\_info \{\\
		char name[50];\\
		char password[20];\\
		enum rights right;\\
	\}\\
	There would be a table for the member info.\\
	When a member logins, his password will be verified and upon
successful login, allowed menu will be displayed.\\
	A function for each menu items will be implemented. Just for
extra precaution, in each function right of the current user will be
checked. If he/she has the correct right to execute that function, then
only the function will be executed otherwise would return silently and
will wait for correct menu choice.
	Library data base will be created as binary file.\\
	It will have a table for the structure of following type.\\
	struct data\_base \{\\
		char author[50];\\
		char name[50];\\
		int copy;\\
	\};\\
	A simple search with full name of author or book will be
implemented.

    \section{Software Tools Required}
    The following software tools will be used:
    \begin{itemize}
    \item pdflatex
    \item vim editor
    \item gcc
    \item ddd
    \end{itemize}
    pdflatex will be used to compile the tex file and vim will be used to edit
    the tex file.
    gcc will be used to compile c code and ddd will be used to debug.
    
\end{document}          
